\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-26 doc/paper.tex
done? typo checking

	% As a general rule, do not put math, special symbols or citations
	% in the abstract
	\begin{abstract} Spreadsheet environments often come equipped with an abundance
		of functions and operations to manipulate data, which users can combine into a
		complex formulae for more sophisticated programs. However, anticipating these
		combinations is difficult, complicating matters for both researchers and
		practitioners who want to study formulae to improve spreadsheet practices.
		Therefore, we developed \toolnameend, a tool that analyzes spreadsheet corpora
		to visualize patterns of function combination as an interactive tree, capable
		of representing both the most common and most anomalous patterns of formula
		construction and their contexts in actual workbooks. Using spreadsheets from
		the Enron corpus, we conduct both a case study and a user study to explore
		\toolnameposs various applications, particularly those in flexible smell
		detection and spreadsheet education.

@@

	Considering the value of spreadsheets and all of these resources to describe
	their use, it becomes necessary that we design tools to better enable the
	exploration of these datasets and simplify the complex concepts that occur in
	spreadsheet design. One such concept is that of formula construction; functions
	are an important part of using spreadsheets efficiently, yet the number of
	their potential combinations quickly becomes massive when you consider that
	there are hundreds of them. Tools, then, that empower people to explore
	questions about which functions are used together in practice have the
	potential to improve the current design of spreadsheets themselves and educate
	new generations of spreadsheets users on how to work best.

@@

		\item [!3] \textbf{Do not attempt to explain formulae.} Though the tool will
		to foster understanding by linking pattern to example, it should not provide a
		precise description of what a complex formula accomplishes. The tool's user
		must infer this on their own.

@@

	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{ifExample}
		\caption{Configurations of the IF function} \label{fig:ifexample} \end{figure}

@@

	\begin{figure}[h] \centering \includegraphics[scale=.75]{lookup-2}
		\includegraphics[scale=.75]{lookup-3} \caption{LOOKUP with two and
			three arguments}  \label{fig:lookups} \end{figure}

@@

	\begin{figure}[h] \centering \includegraphics[scale=.75]{vlookup}
		\includegraphics[scale=.75]{hlookup} \caption{VLOOKUP and HLOOKUP with
			four arguments} \label{fig:vhlookups}\end{figure}

@@

	\begin{wrapfigure}{O}{.25\textwidth}
		\centering \includegraphics{SUM}  \caption{An abundance of parameters in SUM.
			Encountering this, P4 remarked, "Woah."} \label{fig:sum} \end{wrapfigure}

@@

	\begin{figure} \centering \includegraphics[scale=.75]{index}
		\caption{A difficult question: how often is MATCH used in both the second and
			third arguments?} \label{fig:index} \end{figure}

>>>>

	% As a general rule, do not put math, special symbols or citations
	% in the abstract
	\begin{abstract} Spreadsheet environments often come equipped with an abundance
		of functions and operations to manipulate data, which users can combine into
		complex formulae. However, anticipating these
		combinations is difficult, complicating matters for both researchers and
		practitioners who want to study formulae to improve spreadsheet practices.
		Therefore, we developed \toolnameend, a tool that analyzes spreadsheet corpora
		to visualize patterns of function combination as an interactive tree, capable
		of representing both the most common and most anomalous patterns of formula
		construction and their contexts in actual workbooks. Using spreadsheets from
		the Enron corpus, we conduct both a case study and a user study to explore
		\toolnameposs various applications, particularly those in flexible smell
		detection and spreadsheet education.

@@

	Considering the value of spreadsheets and all of these resources to describe
	their use, it becomes necessary that we design tools to better enable the
	exploration of these datasets and simplify the complex concepts that occur in
	spreadsheet design. One such concept is that of formula construction; functions
	are an important part of using spreadsheets efficiently, yet the number of
	potential combinations between them quickly becomes massive when you consider that
	there are hundreds of them. Tools, then, that empower people to explore
	questions about which functions are used together in practice have the
	potential to improve the current design of spreadsheets themselves and educate
	new generations of spreadsheets users on how to work best.

@@

		\item [!3] \textbf{Do not attempt to explain formulae.} Though the tool will
		to foster understanding by linking pattern to example, it will not try to be
		an explanatory tool that articulates what a complex formula accomplishes. Rather,
		we will provide the structure and context, and the user	must infer this on their own.

@@

	\begin{figure}[h] \centering \includegraphics[scale=.9]{ifExample}
		\caption{Configurations of the IF function} \label{fig:ifexample} \end{figure}

@@

	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{lookup-2}
		\includegraphics[width=.5\textwidth]{lookup-3} \caption{LOOKUP with two and
			three arguments}  \label{fig:lookups} \end{figure}

@@

	\begin{figure}[h] \centering \includegraphics[width=.5\textwidth]{vlookup}
		\includegraphics[width=.5\textwidth]{hlookup} \caption{VLOOKUP and HLOOKUP with
			four arguments} \label{fig:vhlookups}\end{figure}

@@

	\begin{wrapfigure}{O}{.25\textwidth}
		\centering \includegraphics[width=.20\textwidth]{SUM}  \caption{An abundance of parameters in SUM.
			Encountering this, P4 remarked, "Woah."} \label{fig:sum} \end{wrapfigure}

@@

	\begin{figure} \centering \includegraphics[width=.4\textwidth]{index}
		\caption{A difficult question: how often is MATCH used in both the second and
			third arguments?} \label{fig:index} \end{figure}
